\large UNet-HCRF Integration for Sequence Labeling on EEG Data

### 2024-12-09 manuscript/slides.tex
edit introduction and model structure

\title[\textcolor{black}{UNet-CRF\_EEG}]{\large
UNet-CRF Integration for Sequence Labeling on EEG Data}

@@

@@

\section[Model Structure]{Model Structure}

\begin{frame}{Model Structure}
\begin{small}
\begin{itemize}
\item An Unet CNN was designed to generated a feature map, and a global
potential for the label.
\item A hidden CRF layer will address the pixel wise label information of the
feature map, then assign a latent label $h_i$ at each pixel.
\item The latent label $h_i$ will contribute the global feature through the
following potetial.
\begin{equation*}
\varphi(y, h_{j}; \delta) = \sum_{a \in Y} \sum_{b \in H} \delta_{a, b}
\cdot \one(y = a) \cdot \one(h_j = b)
\end{equation*}
\item The jointly probability distribution of the model
\begin{equation*}
\begin{split}
\Phi(y, \hb, \xb; \theta) &= \underbrace{
\sum_{j \in \nu} \phi(h_j, x_j; \omega)
+ \sum_{i \neq j} \psi(h_i, h_j, x_i, x_j; \eta)}_{
% \propto \log\PP(\hb \vert \xb; \theta)
\textrm{Measures log-likelihood $\log\PP(\hb \vert \xb; \theta)$}} \\
&+ \underbrace{
\sum_{j \in \nu} \varphi(y, h_j, x_j; \delta) + \vartheta(y, \xb; \varpi)}_{
% \propto \log\PP(y | \hb,  \xb; \theta)
\textrm{Measures log-likelihood $\log\PP(y \vert \hb, \xb; \theta)$}}
\end{split}
\end{equation*}
\end{itemize}
\end{small}
\end{frame}

>>>>

\title[\textcolor{black}{UNet-HCRF\_EEG}]{\large
UNet-HCRF Integration for Sequence Labeling on EEG Data}

@@

\begin{frame}{Introduction}
\begin{itemize}
\setlength{\itemsep}{1.5em}
\item Sequence labeling tasks are crucial for healthcare, where accurate and
timely data classification can significantly impact patient outcomes.
\item Deep learning has recently emerged as a powerful tool for sequence
labeling.
\item Conditional random fields (CRFs) have been employed for modeling label
dependencies, demonstrating promising results.
\end{itemize}
\end{frame}

\section[Methods]{Methods}

\begin{frame}{CNN-HCRF Model Structure}
\begin{itemize}
\item An UNet CNN was designed to generate a feature map, and a global
potential for the label.
\item A hidden conditional random field (HCRF) layer processes the pixel-wise
label information from the feature map, assigning a latent label $h_i$ to each
pixel.
\item The latent label $h_i$ contributes to the global feature through the
following potetial:
\begin{equation*}
\varphi(y, h_{j}; \delta) = \sum_{a \in Y} \sum_{b \in H} \delta_{a, b}
\cdot \one(y = a) \cdot \one(h_j = b),
\end{equation*}
where $\delta_{a,b}$ denotes the likelihood of class label $y = a$
containing a joint with hidden state $h_j = b$, learned during training.
\end{itemize}
\end{frame}

\begin{frame}{CNN-HCRF Model Structure (cont.)}
\begin{small}
\begin{itemize}
\item Unary potential $\phi(h_j, x_j; \omega)$: Measures the likelihood of the
local feature $x_j$ is assigned as the hidden part state $h_j$, whose parameter
$\omega$ is learned by end-to-end CNN-UNet structure.
\item Binary potential $\psi(h_i, h_j, x_i, x_j; \eta)$: Balances the hidden
label compatibility of the neighboring pixels $p$ on the feature image 
$\Fb(\Ib)$:
\begin{align*}
\psi(h_i, h_j, x_i, x_j; \eta) &= \mu(h_i, h_j) \Bigg[
\omega_1 \exp \left(
-\frac{\left\lvert p_i - p_j \right\rvert^2}{2\eta_\alpha^2}
-\frac{\left\lvert \Fb_i(\Ib) - \Fb_j(\Ib) \right\rvert^2}{2\eta_\beta^2}
\right) \\
&+ \omega_2 \exp \left(
- \frac{\left\lvert p_i - p_j \right\rvert^2}{2 \eta_\gamma^2}
\right)
\Bigg],
\end{align*}
where the parameters $\eta_\alpha$, $\eta_\beta$ and $\eta_\gamma$ control the
influence of the corresponding feature spaces.
\item Global potential $\vartheta(y, \xb; \varpi)$: Measures the compatibility
of class label $y$ and the global feature vector $x_0$ of the whole action,
whose parameter $\varpi$ will be learned during training process.
\end{itemize}
\end{small}
\end{frame}

\begin{frame}{CNN-HCRF Model Structure (cont..)}
Let $y$ represent the corresponding label of the input image $\xb$.
The jointly probability distribution of the HCRF model is:
\begin{align*}
\Phi(y, \hb, \xb; \theta) &= \underbrace{
\sum_{j \in \nu} \phi(h_j, x_j; \omega) +
\sum_{i \neq j} \psi(h_i, h_j, x_i, x_j; \eta)}_{
% \propto \log\PP( \hb \vert \xb; \theta)
\textrm{Measures log-likelihood $\log\PP(\hb \vert \xb; \theta)$}} \\
& + \underbrace{
\sum_{j \in \nu} \varphi(y, h_j, x_j; \delta) + \vartheta(y, \xb; \varpi)}_{
% \propto \log\PP(y | \hb, \xb; \theta)
\textrm{Measures log-likelihood $\log\PP(y \vert \hb, \xb; \theta)$}}
\end{align*}
\end{frame}

%\begin{frame}{Model Structure}
%\begin{small}
%\begin{itemize}
%\item An Unet CNN was designed to generated a feature map, and a global
%potential for the label.
%\item A hidden CRF layer will address the pixel wise label information of the
%feature map, then assign a latent label $h_i$ at each pixel.
%\item The latent label $h_i$ will contribute the global feature through the
%following potetial.
%\begin{equation*}
%\varphi(y, h_{j}; \delta) = \sum_{a \in Y} \sum_{b \in H} \delta_{a, b}
%\cdot \one(y = a) \cdot \one(h_j = b)
%\end{equation*}
%\item The jointly probability distribution of the model
%\begin{equation*}
%\begin{split}
%\Phi(y, \hb, \xb; \theta) &= \underbrace{
%\sum_{j \in \nu} \phi(h_j, x_j; \omega)
%+ \sum_{i \neq j} \psi(h_i, h_j, x_i, x_j; \eta)}_{
%% \propto \log\PP(\hb \vert \xb; \theta)
%\textrm{Measures log-likelihood $\log\PP(\hb \vert \xb; \theta)$}} \\
%&+ \underbrace{
%\sum_{j \in \nu} \varphi(y, h_j, x_j; \delta) + \vartheta(y, \xb; \varpi)}_{
%% \propto \log\PP(y | \hb,  \xb; \theta)
%\textrm{Measures log-likelihood $\log\PP(y \vert \hb, \xb; \theta)$}}
%\end{split}
%\end{equation*}
%\end{itemize}
%\end{small}
%\end{frame}

@@
